Legends for supplementary material

### 2019-03-08 Manuscript/Figures/figure_legends.Rmd
added legends

>>>>

**Figure 5. Line plots comparing models using SMOTE resampling with distance-type predictors.** Model performances were evaluated using F1-score, MCC, and balanced accuracy for each of the 4 data resolutions, across both the GM12878 (red, solid line) and K562 (blue; dashed line) cell lines. For a given metric, each point represents a model applied to a particular resolution with distance type predictors for the feature space, after which the SMOTE algorithm was used to create balanced classes on the trianing set.

### 2019-03-08 Manuscript/Supplementary/supplementary_legends.Rmd
added legends

>>>>

**Figure 5. Line plots comparing models using the remaining resampling techniques with distance-type predictors.** Model performances were evaluated using F1-score, MCC, and balanced accuracy for each of the 4 data resolutions, across both the GM12878 (red, solid line) and K562 (blue; dashed line) cell lines. For a given metric, each point represents a model applied to a particular resolution with distance type predictors for the feature space, after which a particular resampling technique was used to create balanced classes on the trianing set, including none (A), random over-sampling (B), and random under-sampling (C).
